---
title: "STAT/MATH 495: Problem Set 07"
author: "Pei Gong"
date: "2017-10-24"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    collapsed: false
    smooth_scroll: false
    df_print: kable
---

```{r setup, include=FALSE}
library(corrplot)
knitr::opts_chunk$set(
  echo = TRUE, fig.width=8, fig.height=4.5, message=FALSE, warning = FALSE
  )
set.seed(76)

# Load packages
library(tidyverse)
library(broom)
library(knitr)

train <- read_csv("data/cs-training.csv") %>% 
  rename(Id = X1)
test <- read_csv("data/cs-test.csv") %>% 
  rename(Id = X1)
submission <- read_csv("data/sampleEntry.csv")
```

Information on the competition can be found [here](https://www.kaggle.com/c/GiveMeSomeCredit/data).



# Collaboration

Please indicate who you collaborated with on this assignment: Tim Lee



# Build binary classifier

Build the binary classifier based on a single predictor variable: `DebtRatio`,
`age`, or `MonthlyIncome`. Justify this choice. 

Fit logistic model on all three potential models
```{r}
model1<-glm(SeriousDlqin2yrs~MonthlyIncome,data=train,family="binomial")
model1 %>% 
  broom::tidy(conf.int=TRUE)
```

```{r}
model2<-glm(SeriousDlqin2yrs~DebtRatio,data=train,family="binomial")
model2 %>% 
  broom::tidy(conf.int=TRUE)
```

```{r}
model3<-glm(SeriousDlqin2yrs~age,data=train,family="binomial")
model3 %>% 
  broom::tidy(conf.int=TRUE)
```


Step2: predict for auc value for all three models. Pick the predictor that returns highest auc value

model1:
```{r}
log_odds_hat <- predict(model1,newdata=test)
p_hat <- 1/(1 + exp(-log_odds_hat))

profiles_train_augmented <- model1 %>% 
  broom::augment() %>% 
  as_tibble() %>% 
  mutate(p_hat = 1/(1+exp(-.fitted)))

library(ROCR)
# This bit of code computes the ROC curve
pred <- prediction(predictions = profiles_train_augmented$p_hat, labels = profiles_train_augmented$SeriousDlqin2yrs)
perf <- performance(pred, "tpr","fpr") 

# This bit of code computes the Area Under the Curve
auc <- as.numeric(performance(pred,"auc")@y.values)
auc
```

model2 
```{r}
log_odds_hat2 <- predict(model2,newdata=test)
p_hat2 <- 1/(1 + exp(-log_odds_hat2))

profiles_train_augmented2 <- model2 %>% 
  broom::augment() %>% 
  as_tibble() %>% 
  mutate(p_hat2 = 1/(1+exp(-.fitted)))

pred2 <- prediction(predictions = profiles_train_augmented2$p_hat2, labels = profiles_train_augmented2$SeriousDlqin2yrs)
perf2<- performance(pred2, "tpr","fpr") 

# This bit of code computes the Area Under the Curve
auc2 <- as.numeric(performance(pred2,"auc")@y.values)
auc2
```

model3 
```{r}
log_odds_hat3 <- predict(model3,newdata=test)
p_hat3 <- 1/(1 + exp(-log_odds_hat3))

profiles_train_augmented3 <- model3 %>% 
  broom::augment() %>% 
  as_tibble() %>% 
  mutate(p_hat3 = 1/(1+exp(-.fitted)))

pred3 <- prediction(predictions = profiles_train_augmented3$p_hat3, labels = profiles_train_augmented3$SeriousDlqin2yrs)
perf3<- performance(pred3, "tpr","fpr") 

# This bit of code computes the Area Under the Curve
auc3 <- as.numeric(performance(pred3,"auc")@y.values)
auc3
```
Out of the three variable, predictor age is the best classifier because it returns the highest auc value, indicating that it has the highest predictive power of the binary outcome. 

```{r}
submission_kaggle<-bind_cols(Id=submission$Id,Probability=p_hat3)
write.csv(submission_kaggle,file="submission.csv",row.names = FALSE)
```

# ROC curve

Based on the ultimate classifier you choose, plot a corresponding ROC curve.


Plot the ROC curve for age.

```{r}
plot(perf, main=paste("Area Under the Curve =", round(auc3, 3)))
abline(c(0, 1), lty=2)
```


# ROC curve for random guessing

Instead of using any predictor information as you did above, switch your predictions to random guesses and plot the resulting ROC curve.

```{r}
#shuffle the SeriousDlqin2yrs column against the dataset so there is no relationship between predictor and y
train_shuffle<-train["SeriousDlqin2yrs"]%>% sample_frac(size = 1, replace = TRUE)
train_hah<-bind_cols(train,train_shuffle)
model4<-glm(SeriousDlqin2yrs1~age,data=train_hah,family="binomial")
```

```{r}
log_odds_hat4 <- predict(model4,newdata=test)
p_hat4 <- 1/(1 + exp(-log_odds_hat4))
profiles_train_augmented4 <- model4 %>% 
  broom::augment() %>% 
  as_tibble() %>% 
  mutate(p_hat4 = 1/(1+exp(-.fitted))) 
  
pred4 <- prediction(predictions = profiles_train_augmented4$p_hat4, 
                   labels =profiles_train_augmented4$SeriousDlqin2yrs1)

perf4 <- performance(pred4, "tpr","fpr") 

# This bit of code computes the Area Under the Curve
auc4 <- as.numeric(performance(pred4,"auc")@y.values)
auc4
plot(perf4, main=paste("Area Under the Curve =", round(auc4, 3)))
abline(c(0, 1), lty=2)
```
